Predicting tree failure likelihood for utility risk mitigation via a novel convolutional neural network

### 2021-01-13 docs/manuscript/manuscript.tex
additions to manuscript outline

\section{Background}
\section{Data}

\section{Methods}

>>>>

\section{Background}

\section{Data and Methods}
\subsection{Image data description}
Based on the  ISA’s Tree Risk Assessment Qualification (TRAQ) protocol, four categories of tree failure likelihood are defined. In this paper we only focus on three:
\begin{itemize}
\item \textbf{Probable}: failure expected under normal weather conditions within a given timeframe
\item \textbf{Possible}: failure expected under extreme weather conditions; but unlikely during normal weather conditions
\item \textbf{Improbable}: failure unlikely either during normal or extreme weather conditions 
\end{itemize}

\subsection{Data pre-processing}

\subsection{Convolutional neural network}
